\chapter{Third-Party Code and Libraries}

\section{Server side libraries}

Ruby on Rails is the base framework I used for my server application, RoR comes packaged with a host of other libraries all used as well. 
\cite{mit}. The library is released using the MIT License 
\cite{rails}. This library was used without modification. 

The packages Kaminari and api-pagination where used to add in pagination to the project
\cite{mit}. Both libraries is released using the MIT License 
\cite{kaminari}. This library was used without modification. 
\cite{paginate}. This library was used without modification. 

The packages RSpec, FactoryGirl, WebMock, spork-rails, guard-spork, and childprocess where all used as part of the testing setup. 
\cite{mit}. All libraries where released under the MIT LIcense.
\cite{rspec}. This library was used without modification. 
\cite{FactoryGirl}. This library was used without modification. 
\cite{WebMock}. This library was used without modification. 
\cite{spork}. This library was used without modification. 
\cite{child}. This library was used without modification. 

The httparty library was used to connect to external APIs
\cite{mit}. This library where released under the MIT LIcense.
\cite{httparty}. This library was used without modification. 

\section{Mobile application libraries}

UICKeyChainStore was used to store personal data using the iOS Key Chain
\cite{mit}. This library where released under the MIT LIcense.
\cite{keychain}. This library was used without modification. 

UniRest was used to retrieve data from the API over HTTP
\cite{mit}. This library where released under the MIT LIcense.
\cite{unirest}. This library was used without modification. 

MBProgressHUD was used to display a progress bar when undertaking certain tasks
\cite{mit}. This library where released under the MIT LIcense.
\cite{progress}. This library was used without modification. 
